---
title: "ReproWithR"
author: "Philip Stapmanns"
date: "3 3 2021"
output: html_document
---

  *Unfortunately my PI didn't want me to use data from my workgroup the data we acquired so far has partially not been published.*  
  *That is why I'll be using a COVID-19 dataset provided by the ECDC for this analysis.*  
  
## 1. Load needed packages
```{r}
library(lubridate)
library(tidyverse)
```
## 2. load the dataset
```{r}
# Data is used from a public dataset by the ECDC https://www.ecdc.europa.eu

covid_data <- read.csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv", na.strings = "", fileEncoding = "UTF-8-BOM", stringsAsFactors = F)
covid_data$date_reported <- mdy(paste0(covid_data$month,"-",covid_data$day,"-",covid_data$year))
```
## 3. basic exploration of the data  
The total number of **positive tested** in the pandemic so far is   
**`r format(sum(covid_data$cases), big.mark = ".")`**  
The total number of **confirmed deaths** in the pandemic so far is   
**`r format(sum(covid_data$deaths), big.mark = ".")`**  

## 4. countries that were hit worst by the pandemic so far
```{r}
analysis <- covid_data %>%
  group_by(countriesAndTerritories)%>%
  summarise(deaths_sum = sum(deaths), daily_max = max(deaths)) %>%
  arrange(desc(deaths_sum))

head(analysis, 10)
```
## 5. visualize the table
```{r}
top_ten <-analysis%>%
  slice_max(n=10, order_by = deaths_sum)

options(scipen=9999)
ggplot(top_ten, aes(reorder(countriesAndTerritories, deaths_sum), deaths_sum)) +
  geom_col() +
  coord_flip() +
  labs(y = "Deaths since begin of pandemic", x = "", title = "Top ten countries with most deaths")
```
  
## 6. Visualize cumulative incidence for 14 days/100.000 inhabitants and total deaths for germany since beginning of the pandemic 
#### Unfortunately, so far, there is no newer data in the dataset for this year. So numbers have dropped of course, yet I wasn't yet able to incorporate this here.
```{r}
germany <- covid_data[covid_data$countriesAndTerritories == "Germany",]

ggplot(germany, aes(x = date_reported, y = as.numeric(Cumulative_number_for_14_days_of_COVID.19_cases_per_100000)))+
  geom_col(fill = "red", alpha = 0.8)+
 theme_minimal(base_size = 14) +
 xlab(NULL) + ylab(NULL) + 
 scale_x_date(date_labels = "%Y/%m/%d") +
  labs(title = "Cumulative 14-day incidence per 100.000 inhabitants", subtitle = "Black line marks current goal for openingstrategies in Germany")+
  geom_hline(yintercept = 35, size = 1)

ggplot(data = germany, aes(x = date_reported, y = as.numeric(deaths)), fill = "black", alpha = 0.2) + 
  geom_col()+
 theme_minimal(base_size = 14) +
 xlab(NULL) + ylab(NULL) + 
 scale_x_date(date_labels = "%Y/%m/%d")+
   labs(title = "Number of deaths per day")
```
